\begin{rubric}{Teaching Experience}
 \entry*[2025/09 -- 2026/04\hfill]%
 \textbf{Adjunct Instructor,} Asian Studies / Political Science
 \par Temple University Japan Campus, Tokyo
\par Classes: \emph{Japan in a Changing World}, \emph{Foreign Governments}
      \par Teaching two classes in the Fall and Winter semesters at Temple University for the Asian Studies and Political Science departments.
%
%
%
 \entry*[2024/04 -- Present\hfill]%
 \textbf{Part-time Lecturer,} Exchange Students from Overseas Program,
 \par Hōsei University, Tokyo, Japan
        \par Classes: \emph{War and Memory in Modern Japan}
        \par Teaching international and Japanese students about Japan's modern history of war and remembrance.
 %
 %
 %
 \entry*[2024/09 -- 2026/03\hfill]%
 \textbf{Part-time Lecturer,} International Studies
 \par Kyōritsu University, Tokyo, Japan
        \par Classes: \emph{Theories of International Relations II, English Writing}
        \par Developed a syllabus for third and fourth-year Japanese undergraduate students introducing the basic theories of international relations such as realism, liberalism, constructivism, and Marxism in the context of concrete examples involving Japan and the rest of the world. I also teach English essay writing to first-year students.
 %
 %
 %
  \entry*[2024/09 -- 2025/03\hfill]%
  \textbf{Part-time Lecturer,} Sociology Department
  \par Daitō Bunka University, Saitama, Japan
        \par Classes: \emph{Current Events in English}
        \par Temporarily filled in for one semester. Teaching second and third-year Japanese students current events in society through the lens of sociology.
 %
 %
 %
 \entry*[2024/09 -- 2024/12\hfill]%
 \textbf{Part-time Lecturer,} IES Abroad
 \par Kanda University of International Studies, Chiba, Japan
        \par Classes: \emph{The Contemporary Economy of Japan}
        \par Temporarily filled in for one semester. I designed and taught a new syllabus introducing the basic history and contemporary elements of Japan's political economy. Alongside lectures, readings, and guest speakers coursework, I organized two field trips related to the history of globalization and state-led innovation.
 %
 %
 %
\entry*[2019/09 -- 2025/02\hfill]%
\textbf{Teaching Assistant (Academic Writing Tutor),}
\par Global Education Center, Waseda University
%
%
%
 \entry*[2023/09 -- 2024/03\hfill]%
 \textbf{Part-time lecturer (English Discussion),}
 \par Tokyo Women's Christian University
         \par Classes: \emph{English Discussion Workshop II}
 %
 %
 %
\entry*[2023/04 -- 2024/03\hfill]%
\textbf{Teaching Assistant (Professor Glenda Roberts),}
\par Graduate School of Asia-Pacific Studies, Waseda University
\end{rubric}
